Praise the people or praise the place? Upper tail human capital in electrifying Sweden

### 2024-01-23 index.qmd
add slides

## Vem är Vem?

## Vem är Karl Lund?

@@

## Firms across the country

@@

## NLP challenges

@@

## Structure using OpenAI API 🤖

## Add coordinates to firms and individuals

@@

Makes use of occupational title, e.g. "Civilingenjör, teknisk fysik" and workplace information, e.g. "Strömsnäs Järnverks A-B".

@@

## Why was classification hard?

## Why is classification easier now?

## What is an embedding?

## What is an embedding?{.unnumbered}

## Use embeddings to cluster skills

## Use clusters to classify individuals into the groups

## Use clusters to classify new skills into the groups

## Cluster firms by location

## You can do it too!

@@

# Appendix {#sec-appendix background-color="#1C9E77" visibility="uncounted"}

@@

```{r}
library(gt)

@@

>>>>

@@

@@

@@

75,000 biographies in 9 volumes of *Vem är Vem?* and 2,400 firms in *Svensk Industrikalender* in a machine readable format for ~ 80 USD.

@@

Makes use of occupational title, e.g. "Civilingenjör, teknisk fysik" and workplace information, e.g. "Strömsnäs Järnverks A-B" to classify individuals into groups.

Result: HISCO code and an industry
:::
::: {.column}

```{python, eval=FALSE, echo=TRUE}
{
  "input": [
    {
      "occupational_title": "Civilingenjör, teknisk fysik",
      "workplace": "Strömsnäs Järnverks A-B"
    },
  ],
  "output": [
    {x
      "hisco_code": "22",
      "industry": "Iron and steel production"
    }
}

@@

## Results: How far do engineers move?

![](assets/eee_map.png){fig-align="center" width=100%}

# Engineers in electrical appliances and machinery move the furthest

![](assets/engineer_distance.png){fig-align="center" width=100%}

# Conclusion{#sec-conclusion background-color="#1C9E77" visibility="uncounted"}

Bifurcated labour market in Sweden; middle-skill workers stay put, high-skill workers move to opportunity both for education and work.

@@

# Appendix{#sec-appendix background-color="#d95f02"}

@@

```{r}
library(gt)
library(tidyverse)

@@

## Vem är Karl Lund?{visibility="uncounted"}

## NLP challenges{visibility="uncounted"}

## Structure using OpenAI API 🤖{visibility="uncounted"}

## Add coordinates to firms and individuals{visibility="uncounted"}

## Firms across the country{visibility="uncounted"}

## Occupational info{visibility="uncounted"}

## Vem är Vem?{visibility="uncounted"}

## Why was classification hard?{visibility="uncounted"}

## Why is classification easier now?{visibility="uncounted"}

## What is an embedding?{visibility="uncounted"}

## What is an embedding?{visibility="uncounted"}

## Use embeddings to cluster skills{visibility="uncounted"}

## Use clusters to classify individuals into the groups{visibility="uncounted"}

## Use clusters to classify new skills into the groups{visibility="uncounted"}

## Cluster firms by location{visibility="uncounted"}

## You can do it too!{visibility="uncounted"}
